---
title: "Lay_Aaron_AssignmentV"
author: "Aaron Lay"
date: "10 1 2022"
output: html_document
---

The project version history is documented under: https://github.com/AaronLay/DSPM_Assignment_V

```{r  warning= FALSE,error=FALSE, message=FALSE}

library(httr)
library(devtools)
library(jsonlite)
library(dplyr)
library(ggplot2)

wd = "C:/Users/aaron/Arbeitsplatz/Uni/M.Sc. Data Science/(1) WiSe_21_22/Data Science Project Management/Assignments"
setwd(wd)

```

The API key is inserted from another .R file 
```{r warning= FALSE}
source(paste(wd,"/TickMas_API.R",sep=""))
```

The first 20 venues in germany are extracted from the API.
```{r}
venues_grmny <- GET(url = "https://app.ticketmaster.com/discovery/v2/venues?",
                    query = list(countryCode = "DE",
                                 locale = '*',
                                 apikey = key))

venue_data <- jsonlite::fromJSON(content(venues_grmny,as = "text"))[["_embedded"]]$venues  %>% select(name,city,postalCode,address,url,location)

venue_data[,2] <- venue_data[,2]
venue_data[,4] <- venue_data[,4]
venue_data[,6:7] <- venue_data[,6]

colnames(venue_data) <- c("name","city","postalCode","address","url","longitude","latitude")

venue_data$longitude <- as.numeric(venue_data$longitude)
venue_data$latitude <- as.numeric(venue_data$latitude)



glimpse(venue_data)

```


To be able to addapt the results to diffrent countries, I created in this regard a felxible function.

```{r }

venues_country <-
  function(countryCode,
           CountryName,
           min_long,
           max_long,
           min_lat,
           max_lat) {
    # The size of a page is defined
    size = 250
    
    # The total number of pages is extracted
    total_pages = content(GET(
      url = "https://app.ticketmaster.com/discovery/v2/venues?",
      query = list(
        countryCode = countryCode,
        locale = '*',
        apikey = key,
        size = 250
      )
    ))$page$totalPages
    
    # The total number of elements is extracted
    n = content(GET(
      url = "https://app.ticketmaster.com/discovery/v2/venues?",
      query = list(
        countryCode = countryCode,
        locale = '*',
        apikey = key,
        size = 250
      )
    ))$page$totalElements
    
    # An empty data frame is created
    venue_data_complete <-
      data.frame(
        name = character(n),
        city = character(n),
        postalCode = character(n),
        adress = character(n),
        url = character(n),
        longitude = character(n),
        latitude = character(n),
        stringsAsFactors = FALSE
      )
    
    # For loop that iterates over all pages
    for (i in 0:(total_pages - 1)) {
      venues_countryX <-
        GET(
          url = "https://app.ticketmaster.com/discovery/v2/venues.json?",
          query = list(
            countryCode = countryCode,
            apikey = key,
            locale = '*',
            size = size ,
            page = i
          )
        )
      if (i < (total_pages - 1)) {
        json_raw = jsonlite::fromJSON(content(venues_countryX, as = "text"))[["_embedded"]]$venues  %>% select(name, city, postalCode, address, url, location)
        
        json_raw[, 2] <- json_raw[, 2]
        json_raw[, 4] <- json_raw[, 4]
        json_raw[, 6:7] <- json_raw[, 6]
        
        venue_data_complete[((i * size) + 1):((i + 1) * size), ] <-
          json_raw
        
      } else {
        json_raw = jsonlite::fromJSON(content(venues_countryX, as = "text"))[["_embedded"]]$venues  %>% select(name, city, postalCode, address, url, location)
        
        json_raw[, 2] <- json_raw[, 2]
        json_raw[, 4] <- json_raw[, 4]
        json_raw[, 6:7] <- json_raw[, 6]
        
        venue_data_complete[((i * size) + 1):n, ] <- json_raw
        
      }
      
      Sys.sleep(0.2)
      
    }
    
    # The geospial columns is formated to a numeric type
    venue_data_complete$longitude <-
      as.numeric(venue_data_complete$longitude)
    venue_data_complete$latitude <-
      as.numeric(venue_data_complete$latitude)
    
    # Locations outside a predefined are are deleted
    venue_data_complete$longitude <-
      ifelse(venue_data_complete$longitude < min_long,
             NA,
             venue_data_complete$longitude)
    venue_data_complete$longitude <-
      ifelse(venue_data_complete$longitude > max_long,
             NA,
             venue_data_complete$longitude)
    
    venue_data_complete$latitude <-
      ifelse(venue_data_complete$latitude < min_lat,
             NA,
             venue_data_complete$latitude)
    venue_data_complete$latitude <-
      ifelse(venue_data_complete$latitude > max_lat,
             NA,
             venue_data_complete$latitude)
    
    # The county plot is created
    ggplot() +
      geom_polygon(
        aes(x = long, y = lat, group = group),
        data = map_data("world", region = CountryName),
        fill = "grey90",
        color = "black"
      ) +
      geom_point(
        data = venue_data_complete,
        aes(x = longitude, y = latitude),
        alpha = 0.5,
        size = 0.5,
        colour = "blue"
      ) +
      theme_void() + coord_quickmap() +
      labs(title = paste("Event locations across ", CountryName),
           caption = "Source: ticketmaster.com") +
      theme(
        title = element_text(
          size = 8,
          face = 'bold',
          hjust = 0.5
        ),
        plot.caption = element_text(face = "italic")
      )
    
  }  

```


Eventlocations from venues in Germany: 

```{r warning= FALSE}
venues_country("DE","Germany",5.866944,15.043611,47.271679,55.0846)
```
Eventlocations from venues in France: 

```{r  warning= FALSE}
venues_country("FR","France",-4.783333,8.216667,42.333333,51.083333)
```

Eventlocations from venues in Norway: 
```{r  warning= FALSE}
venues_country("NO","Norway",4.66269,30.94355,58.08878,80.49493)
```
